Design and Implementation of Probabilistic Programming Language Anglican

### 2017-03-16 paper/paper.tex
finally got quoting right

\ttfamily
\DeclareFontShape{OT1}{lmtt}{m}{it}
     {<->sub*lmtt/m/sl}{}
\iftoggle{full}{
\lstdefinestyle{default}{language=Anglican,basicstyle=\ttfamily\small, columns=flexible, showstringspaces=false}
}{
\lstdefinestyle{default}{language=Anglican,basicstyle=\linespread{0.842}\ttfamily\small, columns=flexible, showstringspaces=false}
}

@@

\acmConference[IFL'16]{Implementation and Application of Functional Programming Languages}{August 2016}{Leuven, Belgium}
\acmYear{2016}
\copyrightyear{2017}

@@

@@

The purpose of probabilistic forms \texttt{sample} and
\texttt{observe} is to interrupt deterministic computation and
transfer control to the inference algorithm.  Practically, this
is achieved by returning a record that represents the state of program execution at the checkpoint, rather than invoking a continuation. The Clojure record used to interrupt execution at 
\texttt{sample} and \texttt{observe} forms are \texttt{anglican.{\linebreak[0]}trap.{\linebreak[0]}sample} and \texttt{anglican.{\linebreak[0]}trap.{\linebreak[0]}observe} respectively. These records contain a unique identifier (which we will discuss in detail in section \ref{sec:addressing}), the arguments to the special form, the continuation, and the state.
\begin{lstlisting}[style=default]
=> (cps-of-expression '(sample dist) 'cont)
(->sample S1 dist cont $state)
=> (cps-of-expression '(observe dist v) 'cont)
(->observe O1 dist v cont $state)
\end{lstlisting}
Here \texttt{->sample} and \texttt{->observe} in the
CPS-transformed expressions are constructors for Clojure
records, and they take values of their fields as arguments.
Calling the continuation resumes the computation.

>>>>

\ttfamily
\DeclareFontShape{OT1}{lmtt}{m}{it}
     {<->sub*lmtt/m/sl}{}
\iftoggle{full}{
\lstdefinestyle{default}{language=Anglican,basicstyle=\ttfamily\small, columns=flexible, showstringspaces=false}
}{
\lstdefinestyle{default}{language=Anglican,basicstyle=\linespread{0.839}\ttfamily\small, columns=flexible, showstringspaces=false}
}

@@

\acmConference[IFL 2016]{Implementation and Application of Functional Programming Languages}{August 2016}{Leuven, Belgium}
\acmYear{2016}
\copyrightyear{2017}

@@

\copyrightyear{2016}
\setcopyright{acmlicensed}
\acmConference[IFL 2016]{Implementation and Application of Functional Programming Languages}{August 2016}{Leuven, Belgium}
\acmISBN{978-1-4503-4767-9/16/08}
\acmPrice{15.00}
\acmDOI{http://dx.doi.org/10.1145/3064899.3064910}

@@

The purpose of probabilistic forms \texttt{sample} and
\texttt{observe} is to interrupt deterministic computation and
transfer control to the inference algorithm.  Practically, this
is achieved by returning a record that represents the state of program execution at the checkpoint, rather than invoking a continuation. The Clojure record used to interrupt execution at 
\texttt{sample} and \texttt{observe} forms are \texttt{anglican.{\linebreak[0]}trap.{\linebreak[0]}sample} and \texttt{anglican.{\linebreak[0]}trap.{\linebreak[0]}observe} respectively. These records contain a unique identifier (which we will discuss in detail in section \ref{sec:addressing}), the arguments to the special form, the continuation, and the state.
\begin{lstlisting}[style=default]
=> (cps-of-expression '(sample dist) 'cont)
(->sample 'S1 dist cont $state)
=> (cps-of-expression '(observe dist v) 'cont)
(->observe 'O1 dist v cont $state)
\end{lstlisting}
Here \texttt{->sample} and \texttt{->observe} in the
CPS-transformed expressions are constructors for Clojure
records, and they take values of their fields as arguments.
Calling the continuation resumes the computation.
